---
title: "brandon_scratch"
author: "Brandon Mannion"
date: "11/27/2018"
output: html_document
---


## other
- implement tangent (derivative-based) adaptive rejection sampler
- INPUTS: sample number
- check density
- check log concave density
- generate enveloping function
- squeezing function
- from sample number, do loop
  - etc. etc. 

## load libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(assertthat)
library(numDeriv)
```
  
  
  
## initial error-checking
- check input domain, D
- check input k, the number of xs to derive tangent
- check input g(x) , it's log form, log-concave, differentiable, etc.
- check input n, the number of values to sample

## function for intersection of tangent lines for x_{j} and x_{j+1}
```{r}

evaluate_z  <- function(x_initial, x_next, log_concave_density) {
        
        assert_that(is.integer(x_initial), msg = "starting x is not a number and/or within D")
        assert_that(is.integer(x_next), msg = "next x is not a number and/or within D")
        
        
        assert_that(
                    
                    
}
        
        
        
        
example_x <- c(1,5,10,12)


```
 
 



