---
title: "brandon_scratch"
author: "Brandon Mannion"
date: "11/27/2018"
output: 
 html_document:
  latex_engine: xelatex
---

# PSEUDO / MISC.
- implement tangent (derivative-based) adaptive rejection sampler
- INPUTS: sample number
- check density
- check log concave density
- generate enveloping function
- squeezing function
- from sample number, do loop
  - etc. etc. 

## initial error-checking
- check input domain, D
- check input k, the number of xs to derive tangent
- check input g(x) , it's log form, log-concave, differentiable, etc.
- check input n, the number of values to sample

# CODE

## load libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
library(assertthat)
library(numDeriv)
```
  
## test variables
```{r}
x <- seq(-10, 10, by=01)

# log-concave example
h <- function(x) {
  return(2*x - 10*log(1 + exp(x)) - 0.5*x^2 + 50)
}

# log-concave example
h <- function(x) {
        return(log(dnorm(x))) 
}

# NOT log-concave
h <- function(x) {
        return(exp(x))    
}
```

## Get intersection of tangent lines for x_{j} and x_{j+1} (FUNCTION)
- equation from paper
    - $z_{j} = \frac{h(x_{j+1}) - h(x_j) - x_{j+1} h'(x_{j+1}) + x_j h'(x_j)}{h'(x_j) - h'(x_{j+1})}$
```{r}
get_z <- function(j, x, h) {
        
        h_xj <- h(x[j])
        h_prime_xj <- grad(h,x[j])
        
        h_xjnext <- h(x[j+1])
        h_prime_xjnext <- grad(h, x[j+1])
  
        z_numerator <- h_xjnext - h_xj - ( x[j+1] * h_prime_xjnext ) + (x[j] * h_prime_xj)
        z_denominator <- h_prime_xj - h_prime_xjnext
        
        z_result <- z_numerator / z_denominator 
        
        ## ASSERTION 
        ## .. check that obtained z intersection is within x
        assert_that(z_result > x[1] && z_result < x[length(x)], msg = "z intersection is outside of X")
       
        return(z_result) 
}
```

## Get all z for all X from 1 to k-1 (FUNCTION)
```{r}
get_z_all <- function(x, h, D) {
       return(unlist(lapply(1:(length(x) - 1), get_z, x, h)))
}
```

## Check log concavity of function (FUNCTION)
```{r}
check_log_concave <- function(j,x,h) {
        
        get_u_integral <- function() {
                uj <- function(t) {
                    tmp_u <- get_u_segment(j,x,h)
                    return(tmp_u$intercept + tmp_u$slope*t)
                }
                fun_u <- function(t) { exp(uj(t)) }
                return(integrate(fun_u, x[j], x[j+1])$value)
        }
        
        # integrate u(x) over x_initial and x_next -> I_u(x)
        u_integral <- get_u_integral()
        
        get_h_integral <- function() {
                fun_h <- function(t) { exp(h(t)) }
                
                return(integrate(fun_h, x[j], x[j+1])$value)
        }
        
        # integrate h(x) over x_initial and x_next -> I_h(x)
        h_integral <- get_h_integral()
        
        cat("u_integral: ", u_integral, "\nh_integral: ", h_integral, "\n")
        
        # check if I_u(x) > I_h(x)
        cat(ifelse(u_integral > h_integral, "upper bound segment > h(x)\n" , "ERROR upper bound segment < h(x)\n"))
        cat("\n")
        
        get_l_integral <- function() {
                lj <- function(t) {
                        tmp_l <- get_l_segment(j,x,h)
                        return(tmp_l$intercept + tmp_l$slope*t)
                }
                fun_l <- function(t) { exp(lj(t)) }
                return(integrate(fun_l, x[j], x[j+1])$value)
        }
        
        # integrate l(x) over x_initial and x_next -> I_l(x)
        l_integral <- get_l_integral()
        
       cat("l_integral: ", l_integral, "\nh_integral: ", h_integral, "\n")
       
       # check if I_l(x) < I_h(x)
       cat(ifelse(l_integral < h_integral, "lower bound segment < h(x)\n" , "ERROR lower bound segment > h(x)\n"))
       
       assert_that(l_integral < h_integral, msg = "lower bound segment is not less than INPUT density")
       assert_that(u_integral > h_integral , msg = "upper bound segment is not greater than INPUT density")
}
```

## Get subset of x and check log-concavity
```{r}
subset_check_log_concave <- function(x_window_size, x, h) {
        
        ## start with window size
        ## choose contiguous regions within X
        ## run check_log_concave FUNCTION on this subset
        ## ... get results on whether satisfies our log concavity conditions 
}
```